\section{Introduction}
\label{chap:intro}
The well known version 1.1 of the HTTP protocol is used since 1999 for browsing the web. It is a protocol that has been reviewed many time to the point that the IETF has split the original RFC (2616\cite{RFC2616}) into six different ones (7230-7235\cite{RFC723x}) describing the whole protocol in details. After more than 15 years of use it was time for a change. All the tricks not to slow the HTTP/1.1 protocol have to be forgotten as on February the 18th 2015, the specification \cite{http2} for the new HTTP protocol HTTP/2 (and HPACK\cite{hpack}), has been formally approved by the IESG and is on the way to become an RFC standard.   \\
The main focus during the development period of the successor of HTTP/1.1 was to improve the performance, and thus provide a better user experience. The performance improvement is based on how the packets are sent over the wire within a HTTP/2 session. HTTP/2 data is sent in binary format and instead of creating a single TCP session per element retrieved, HTTP/2 create TCP streams that are multiplexed and that can be prioritized. The goal of this technique is to reduce the high number of TCP sessions created every time a user access a web page. Concerning security, HTTP/2 will not make the use of TLS mandatory. However, leading browsers firms, Mozilla Firefox and Google Chrome have already mentioned that HTTP/2 will only be implemented over TLS. Thus ensuring that the data will be encrypted between two end parties. HTTP/2 introduces several other new features that will be presented in this paper. \\
There are already web client and server implementations\cite{http2-imp} that support the final HTTP/2 specification. This research is intending to show what are the impacts of implementing HTTP/2 with TLS compared to HTTPS in a large environment. The implemented server will be tested with a high number of virtual clients located at different places around the world to outline the impact of the round trip time (RTT) on both version of the protocol and to see which performs the best. The research will draw conclusions on what impacts does the new protocol can have on large web service providers infrastructure.